Fluoroproj: Title to be decided later

### 2023-04-03 manuscript/manuscript.qmd
added some text to manuscript, and updated scripts
added notes and code to manusript for in situ/extract compare

@@

>>>>

This worked well until the fluorometer gave us problems.

With culture, first look not very linear, but split out but green, cyan, and mixed each grouping shows linear relationship between extracted and in situ turner.  Might not matter that different waterbodies would be in different green/cyano/mix classes.  But the pattern between extracted and in situ/handheld flouros should be similar.  Different pattern with any handheld/in situ would suggest it not perfomring well.

```{r comparisons}
library(readr)
library(dplyr)
library(ggplot2)

prelim_ext_chl <- read_csv(here::here("data/raw/extracted chl/extracted_chl_fluororproj_prelimanary_test_2023_3_29.csv")) |>
  group_by(waterbody) |>
  summarize(extracted = mean(value, na.rm = TRUE)) |>
  arrange(waterbody)
prelim_in_viv <- read_csv(here::here("data/raw/trilogy in vivo/trilogy in vivo 2023_03_28_fresh.csv")) |>
  mutate(waterbody = case_when(waterbody == "culture_aba" ~
                                 "culture_ana",
                               TRUE ~ waterbody))|>
  group_by(waterbody) |>
  summarize(in_vivo = mean(value, na.rm = TRUE)) |>
  arrange(waterbody)

all <- bind_cols (prelim_ext_chl, prelim_in_viv) |>
  select(culture = waterbody...1, extracted, in_vivo) |>
  filter(!is.na(culture)) |>
  mutate(class = case_when(culture == "culture_ana" ~
                             "cyano",
                           culture == "culture_ana_pando" ~
                             "mix",
                           culture == "culture_mic" ~
                             "cyano",
                           culture == "culture_mic_ana" ~
                             "cyano",
                           culture == "culture_mic_pando" ~
                             "mix",
                           culture == "culture_pando" ~
                             "greens",
                           culture == "culture_pedia" ~
                             "greens",
                           culture == "culture_pedia_pando" ~
                             "greens",
                           culture == "culture_mic_ana_pando_pedia" ~
                             "mix",
                           TRUE ~ culture))

ggplot(all, aes(x = extracted, y = in_vivo, color = class)) +
  geom_point(size = 5)
```

@@

```{r}
library(dplyr)
library(readr)
read_csv("../data/cleaned_fluoroproj_data.csv")
```
